The Transition from Massive Metal Free Stars to Dwarf Galaxies

### 2011-03-03 ms.tex
Changing the SFH plots to have the time axis as time instead of stellar age.

Over the past decade, these works have refined the general picture of
inhomogenous metal enrichment and the transition to Pop II star
formation, and here we give a brief overview of its development.
Considering only Pop III star formation, \citeauthor{Yoshida04}
calculated that Pop III stars can raise the mean metallicity to $-4.5
\la$ [Z/H]\footnote{We use the conventional notation, [Z/H] $\equiv
  \log(Z/H) - \log(Z_\odot/H_\odot)$.} $\la -3.5$ by redshift 15 in
the upper limit where all metal-free stars have $M = 200 \Ms$ and
produce PISNe.  Considering both Pop III and II star formation,
\citeauthor{Scannapieco03} found that the transition between the two
modes is a gradual process where both modes are coeval, confirmed by
most of the later works.  Because the host galaxies have small masses
and are subject to negative radiative feedback through photo-heating
and photo-dissociation, the minimum halo mass gradually increases with
the radiation background intensity, which
\citeauthor{Furlanetto05_Reion} found to delay metal enrichment and
place it closer to the epoch of reionization.  \citeauthor{Trenti09}
noted that underdense regions of the universe are still pristine at
$z=6$ with Pop III stars still forming at these late epochs.  This
group later expanded on these results to find that Pop II SFR becomes
dominant at $z>25$ in the buildup of a MW-type halo.  Furthermore they
stress the importance of a photo-dissociating radiation background
that reduces enrichment by PISNe and increases the importance of
metal-rich galactic outflows, where only $10^{-4} - 10^{-2}$ of PISN
ejecta ends up in EMP stars with $M > 0.9 \Ms$.

@@

\begin{figure*}
  \epsscale{2.0}
  \plotone{sfh1.eps}
  \epsscale{1.0}
  \caption{\label{fig:SFH} The scatter plots show the Pop II star
    formation history as a function of stellar age $t_\star$ with
    respect to metallicity for the 10 most massive halos.  Halo 8 is
    not shown because it contains no stars.  Each circle represents a
    star particle, whose area is proportional to its mass.  The open
    circles in the upper right represent $M = 10^3$, $10^4$, and
    $10^5$ \Ms.  The dashed lines in the Halo 0 panel guide the eye to
    two stellar populations that were formed in two satellite halos,
    merging at $z=7.5$.  The upper histogram shows the star formation
    rate with each bar representing 5 Myr.  The right histogram
    depicts the Pop II metallicity distribution function.}
\end{figure*}

Here we present the properties of the metal-enriched stellar
population.  The SFHs of the 10 most massive haloes are shown in
Fig. \ref{fig:SFH} in the plane of stellar age $t_\star$ and
metallicity as scatter plots with each point representing a star
particle and its size proportional to its mass.  Collapsing the data
along the time and metallicity axes gives the metallicity distribution
function (MDF) and star formation rate, respectively, also shown in
the Figure.

@@

Mass-to-light ratios are crucial in interpreting observations when
connecting the galaxy to its DM halo, and ultimately to models of
galaxy formation.  For this paper, we use a simple model to calculate
the total stellar luminosity of each galaxy.  In a later paper, we
will follow up with more sophisicated models to determine more
accurate observables.  Stars in each particle are treated an
instantaneous burst.  Using the empirical law of main sequence
lifetime $t_{\rm MS} \propto M^{-5/2}$, the maximum stellar mass in
such a system is dependent only on its age, $M_{\rm up} = (t_\star /
10\;\mathrm{Gyr})^{-2/5}$.  Then combining another scaling law $L
\propto M^{7/2}$ and the Salpeter IMF $\psi(M) \propto M^{-\alpha}$,
%
\begin{eqnarray}
  \label{eqn:lum}
  L/M_\odot &=& \int_{M_{\rm lo}}^{M_{\rm up}} \psi(M) L(M) dM \nonumber\\
      &\simeq& M_{\rm up}^{9/2-\alpha} (9/2 - \alpha)^{-1},
\end{eqnarray}
where we set $M_{\rm lo} \equiv 0$ because it is negligible in the
luminosity.  Then the galaxy luminosity is the sum of all star
particle luminosities, which we plot in Fig. \ref{fig:Lstar} with
respect to halo mass.

@@

@@

\halo{4} A nearby minihalo initially enriched the most massive
progenitor, triggering Pop II star formation without hosting a Pop III
star at $z=15$ when the halo mass was only $5 \times 10^6 \Ms$.  This
halo experiences a series of major and minor mergers at $z > 10$ and
very little afterwards.  The lack of mergers allows a gas and stellar
disc to form, unlike all of the other galaxies in the simulation.  SNe
feedback creates a bipolar outflow, perpendicular to the disc, that
enriches the surrounding IGM but not the halo itself.

>>>>

Over the past decade, these works have refined the general picture of
inhomogenous metal enrichment and the transition to Pop II star
formation, and here we give an overview of its development.
Considering only Pop III star formation, \citeauthor{Yoshida04}
calculated that Pop III stars can raise the mean metallicity to $-4.5
\la$ [Z/H]\footnote{We use the conventional notation, [Z/H] $\equiv
  \log(Z/H) - \log(Z_\odot/H_\odot)$.} $\la -3.5$ by redshift 15 in
the upper limit where all metal-free stars have $M = 200 \Ms$ and
produce PISNe.  Considering both Pop III and II star formation,
\citeauthor{Scannapieco03} found that the transition between the two
modes is a gradual process where both modes are coeval, confirmed by
most of the later works.  Because the host galaxies have small masses
and are subject to negative radiative feedback through photo-heating
and photo-dissociation, the minimum halo mass gradually increases with
the radiation background intensity, which
\citeauthor{Furlanetto05_Reion} found to delay metal enrichment and
place it closer to the epoch of reionization.  \citeauthor{Trenti09}
noted that underdense regions of the universe are still pristine at
$z=6$ with Pop III stars still forming at these late epochs.  This
group later expanded on these results to find that Pop II SFR becomes
dominant at $z>25$ in the buildup of a MW-type halo.  Furthermore they
stress the importance of a photo-dissociating radiation background
that reduces enrichment by PISNe and increases the importance of
metal-rich galactic outflows, where only $10^{-4} - 10^{-2}$ of PISN
ejecta ends up in EMP stars with $M > 0.9 \Ms$.

@@

\begin{figure*}
  \epsscale{2.0}
  \plotone{sfh1.eps}
  \epsscale{1.0}
  \caption{\label{fig:SFH} The scatter plots show the Pop II star
    formation history as a function of time with respect to
    metallicity for the 10 most massive halos.  Halo 8 is not shown
    because it contains no stars.  Each circle represents a star
    particle, whose area is proportional to its mass.  The open
    circles in the upper right represent $M = 10^3$ and $10^4$ \Ms.
    The dashed lines in the Halo 0 panel guide the eye to two stellar
    populations that were formed in two satellite halos, merging at
    $z=7.5$.  The upper histogram shows the star formation rate with
    each bar representing 5 Myr.  The right histogram depicts the Pop
    II metallicity distribution function.}
\end{figure*}

Here we present the properties of the metal-enriched stellar
population.  The SFHs of the 10 most massive haloes are shown in
Fig. \ref{fig:SFH} in the plane of formation time and metallicity as
scatter plots with each point representing a star particle and its
size proportional to its mass.  Collapsing the data along the time and
metallicity axes gives the metallicity distribution function (MDF) and
star formation rate, respectively, also shown in the Figure.

@@

Mass-to-light ratios are crucial in interpreting observations when
connecting the galaxy to its DM halo, and ultimately to models of
galaxy formation.  For this paper, we use a simple model to calculate
the total stellar luminosity of each galaxy.  In a later paper, we
will follow up with more sophisicated models to determine more
accurate observables.  Stars in each particle are treated an
instantaneous burst.  Using the empirical law of main sequence
lifetime $t_{\rm MS} \propto M^{-5/2}$, the maximum stellar mass in
such a system is dependent only on its age $t_\star$, so $M_{\rm up} =
(t_\star / 10\;\mathrm{Gyr})^{-2/5}$.  Then combining another scaling
law $L \propto M^{7/2}$ and the Salpeter IMF $\psi(M) \propto
M^{-\alpha}$,
%
\begin{eqnarray}
  \label{eqn:lum}
  L/M_\odot &=& \int_{M_{\rm lo}}^{M_{\rm up}} \psi(M) L(M) dM \nonumber\\
      &\simeq& M_{\rm up}^{9/2-\alpha} (9/2 - \alpha)^{-1},
\end{eqnarray}
where we set $M_{\rm lo} \equiv 0$ because it is negligible in the
luminosity.  Then the galaxy luminosity is the sum of all star
particle luminosities, which we plot in Fig. \ref{fig:Lstar} with
respect to halo mass.

@@

\halo{0} \textbf{Early time metal-rich stars.}

@@

\halo{4} A nearby minihalo initially enriched the most massive
progenitor, triggering Pop II star formation without hosting a Pop III
star at $z=15$ when the halo mass was only $5 \times 10^6 \Ms$.  This
halo experiences a series of major and minor mergers at $z > 10$ and
very little afterwards.  The lack of mergers allows a gas and stellar
disc to form, unlike all of the other galaxies in the simulation.  SNe
feedback creates a bipolar outflow, perpendicular to the disc, that
enriches the surrounding IGM but not the halo itself.  \textbf{Metal
  poor stars at late times from minor merger.}
